One of the methods reviewed in this paper is Schism \cite{schism}. Without considering implementation details, the core idea of Schism is to assign a special weight to each edge, referred to as the request weight (r-weight). The r-weight of an edge is increased every time the corresponding edge is traversed during query execution. As a result, frequently accessed edges gradually obtain higher weights. Instead of minimizing the number of inter-storage edges or the size of the edge cut, Schism aims to minimize the total weight of the cut. Therefore, edges with high r-weights, representing frequently accessed relationships, are more likely to be placed within the same storage node, while rarely accessed edges are allowed to remain between partitions.

Another workload-aware partitioning method considered in this paper is WAWPart \cite{wawpart}. Although the original work does not explicitly discuss Schism and does not provide a direct comparison with it, WAWPart is based on a similar concept: assigning r-weights to edges and increasing these weights according to query usage. The main difference is that WAWPart does not increase the weights of all traversed edges equally. Instead, the increase depends on the traversal order, where edges encountered earlier receive larger weight increments, while later edges receive smaller increments. The partitioning objective remains the same: minimizing the total weight of the cut.

The similarity between Schism and WAWPart raises the question of their relative effectiveness and whether workload-aware optimization provides significant advantages compared with traditional minimum-cut partitioning approaches.

To utilize the optimization principles of the previously described workload-aware methods, an algorithm capable of minimizing weighted cuts is required. A suitable candidate is METIS \cite{MetisOG}, a state-of-the-art graph partitioning framework for minimizing edge cuts.

METIS extensively utilizes the Kernighan--Lin (KL) refinement algorithm, which evaluates the benefit of moving a vertex to another partition using the following heuristic:

\begin{equation*}
g_v = \sum_{(v,u) \in E \wedge P[v] \neq P[u]} w(v,u) - \sum_{(v,u) \in E \wedge P[v] = P[u]} w(v,u).
\end{equation*}

This heuristic represents the difference between the total weight of edges connecting a vertex to external partitions and the total weight of edges connecting it to its current partition. In other words, KL inherently minimizes the total weight of the cut and therefore can be applied as a refinement stage after workload information has been collected.

However, METIS has relatively high computational overhead due to its multilevel coarsening, initial partitioning, and uncoarsening phases. Therefore, in this work, these phases are replaced with the streaming graph partitioning algorithm Fennel. Due to the nature of streaming partitioning, Fennel alone cannot perform workload-aware partitioning because vertices and edges are assigned during graph loading, before their future usage patterns are known. Workload-aware behavior can only be introduced if additional semantic information about vertices is available or if the graph is reloaded together with workload-derived information. Such approaches are outside the scope of this paper.

Also our experiments has shown Fennel indeed provide good partitioning that can be used for refinement by KL without requiring large amount of iterations of it.

Therefore, the complete partitioning process is divided into three phases:

\begin{enumerate}
\item Initial graph loading, where vertices are distributed using Fennel or random partitioning;
\item Workload application, where queries are executed and edge usage information is collected;
\item Iterative refinement using Schism, WAWPart, or no refinement.
\end{enumerate}
