
A distinctive feature of the presented Teragraph computing complex is deep hardware support for associative processing. This is expressed in the fact that at all levels of complex software, data storage is implemented in large-scale associative memory, and thanks to the microprocessor core with the discrete mathematics instruction set DISC, the problem of associative-address translation is essentially solved.

For each of the proposed eight structural hierarchy levels, its purpose, composition, and functional features are shown. The concept of resource distribution and isolation for ensuring multi-user access within the cloud approach is briefly presented. Currently, development of the TeraCloud cloud platform and the set of system and application libraries for the complex is being completed.

The Graph Processor Cores is a doubled core with Computing Processing Element and Structure Processing Element, demonstrates heterogeneous efficiency. On one hand, it surpasses the general-purpose CPU by 12 times in clock efficiency when processing sequential data. On the other hand, GPC's performance when working with random keys is 2-4 times lower than that of optimized software data structures on the same CPU, even accounting for the frequency difference.

The key problem is a technological limitation: achieving parity across all operations requires a frequency of 1800 MHz, which is unattainable for modern domestic FPGA and ASIC processes. Therefore, the path of simple frequency scaling for the B+ tree architecture is a dead end.

This necessitates a fundamentally new approach. The development of hybrid data structures is required, combining the efficiency of trees for sequential operations with high-speed handling of random keys. The architecture must include optimized cache memory with intelligent prefetching, mechanisms for speculative execution of traversal operations, and pipelined processing to hide memory access latencies. A critical requirement becomes the transition to multi-threaded and multi-context architectures with fast context switching, which will allow for the most efficient utilization of processor resources when working with irregular graph structures.

The Teragraph system represents a novel approach to graph processing architecture, combining specialized hardware for discrete mathematics operations with traditional computing elements in a heterogeneous configuration. Future work will focus on expanding the instruction set, improving memory hierarchy efficiency, and developing advanced programming tools for the platform.