% !TeX encoding = utf-8
% !TeX program = pdflatex
%% Tsinghua Science and Technology (Tsinghua Sci Technol) - LaTeX Template

\documentclass{TST}

% Исправляем отступы для биографий
\makeatletter
% % Увеличиваем ширину области под фотографию
\def\@TSTBIOhangwidth{1.3in}  % было 1.1in
% Увеличиваем глубину (высоту) области под фотографию  
\def\@TSTBIOhangdepth{1.5in}  % было 1.25in
% Увеличиваем размер фотографии
\def\@TSTBIOphotowidth{1.0in}  % было 1in
\def\@TSTBIOphotodepth{1.25in}  % было 1.25in
\makeatother


\newcommand{\blu}[1]{\textcolor{blue}{#1}}

\TSTsetup{
type      = {Research Article},
doi       = {xxxx},
title     = {Heterogeneous Computational Platform for Parallel Graph Processing},
author    = {Aleksey Yu. Popov\,\cor{}, Stanislav V. Ibragimov, Maxim P. Kalitventsev, Mikhail A. Geine, Jiajian Li, Andrey A. Belevantsev},
runauthor = {A. Yu. Popov, S. V. Ibragimov, M. P. Kalitventsev, M. A. Geine, J. Li, Andrey A. Belevantsev},
abstract  = {
Graph models represent one of the most promising directions for developing data analytics and artificial intelligence systems. Research in this field encompasses not only classical graphs but also complex types such as hypergraphs and metagraphs. The scale and complexity of emerging graph processing tasks necessitate the development of specialized hardware-software solutions to enhance the efficiency of existing computing systems for such workloads. This paper presents the architecture and operational features of the Teragraph computing complex and its cloud platform, designed for processing large-scale graphs. The fundamental principle embedded in the system architecture is the implementation of a multi-level associative memory subsystem, which significantly influences software development methodology and operational characteristics. We provide a systematic description of the hardware and software structure of the computing complex, presenting key technical solutions that enable implementation of large-scale associative memory based on DDR4 SDRAM addressable memory. The associative-address translation for accessing such storage is implemented through the trace processing unit of the Leonard Euler microprocessor. Additionally, the paper describes enhancements to the network interaction subsystem based on a bidirectional ring topology and high-speed 100Gb Ethernet links.
},
keywords  = {computing system, graph processing, discrete mathematics instruction set, associative processing, computing accelerator, heterogeneous architecture},
copyright = {The Author(s)},
received  = 2025-12-14,
revised   = 2025-12-xx,
accepted  = 2025-12-xx,
}

\address{Alexey Yu. Popov, Stanislav V. Ibragimov, Maxim P. Kalitventsev, Mikhail A. Geine, Jiajian Li are with Bauman Moscow State Technical University, Moscow, 105005, Russian Federation. E-mail: alexpopov@bmstu.ru}
\address{Andrey A. Belevantsev is with the Federal State Budgetary Institution of Science Institute for System Programming of the Russian Academy of Sciences (ISP RAS), Moscow, 109004, Russia. Phone: +7(495) 912-07-54 (ext. 400), E-mail: info-isp@ispras.ru}

% Добавьте в преамбулу документа настройки для листингов
\usepackage{listings}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18} % Укажите версию совместимости
\usepackage{tikz}
\usepackage{graphicx}

\lstset{
   basicstyle=\fontsize{4}{5}\selectfont\ttfamily, % Экстремально маленький
   numbers=none,
   frame=none,
   backgroundcolor=\color{white},
   breaklines=true,
   xleftmargin=0pt,
   xrightmargin=0pt,
   aboveskip=1pt,
   belowskip=1pt,
   % numbers=left,
   % numberstyle=\tiny\color{black},   
   columns=fullflexible,
}

% Настройка подписей листингов - выравнивание по левому краю
\captionsetup[lstlisting]{
    format=hang, % Выравнивание по левому краю
    justification=raggedright, % Выравнивание по левому краю
    singlelinecheck=false, % Не центрировать короткие подписи
    labelfont=bf, % Жирный шрифт для метки
    labelsep=space, % Разделитель между метки и текстом
    skip=5pt, % Отступ от листинга
    belowskip=5pt, % Отступ снизу
    font=small % Размер шрифта подписи
}

\begin{document}

\maketitle

% % Сноска о финансировании на первой странице
% \footnotetext{Funding: This research was supported by the Russian Science Foundation grant No. 25-11-90002, \url{https://rscf.ru/project/25-11-90002/}.}

\section{Introduction}
\input{intro_en}
\section{Architectural Design Methodology}
\input{chap1_en}

\section{Conclusion}
\input{conclusion_en}

\section*{Acknowledgments}
This research was supported by the Russian Science Foundation grant No. 25-11-90002, \url{https://rscf.ru/project/25-11-90002/}

\section*{Declaration of Competing Interest}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\bibliographystyle{TSTbib}
\bibliography{export-data}

\section*{Author Biography}

\begin{biography}[popov]{Alexey Yu. Popov} 
Professor, Doctor of Science at Bauman Moscow State Technical University, Russia. Research interests: heterogeneous computing systems, graph processing architectures, discrete mathematics acceleration, and high-performance computing. Published over 60 papers; leads Teragraph project.
\end{biography}

\vspace{0.5cm}

\begin{biography}[ibragimov]{Stanislav V. Ibragimov}
Senior Lecturer at the Department of Computer Systems and Networks, Bauman Moscow State Technical University. His research focuses on network architectures for high-performance computing, distributed systems, and hardware-software co-design.
\end{biography}

\vspace{0.5cm}

\begin{biography}[kalitventsev]{Maksim P. Kalitventsev}
M.Sc., PhD student at Bauman Moscow State Technical University. Specializes in Network-on-Chip (NoC) architectures, simulation modeling, and hardware verification (UVM). Research focuses on communication fabrics for large-scale graph processing systems.
\end{biography}

\vspace{0.5cm}

\begin{biography}[geine]{Mikhail A. Geine}
M.Sc., PhD student and Research Engineer at Bauman Moscow State Technical University. His research interests lie in graph query languages, specialized DBMS, and their application for efficient data management and analytics on heterogeneous supercomputer architectures.
\end{biography}

\vspace{0.5cm}

\begin{biography}[li]{Jiajian Li}
Junior Research Fellow at Bauman Moscow State Technical University, specializing in graph-based knowledge structures and artificial intelligence. His research focuses on the development of semantic and event-driven models for intelligent systems. 
\end{biography}

\vspace{0.5cm}

\begin{biography}[belevancev]{Andrey A. Belevantsev}
Andrey Belevantsev is a Corresponding Member of the Russian Academy of Sciences (RAS, 2025), Doctor of Physical and Mathematical Sciences, and Professor of RAS. His research focuses on program optimizations, static analysis, safe compilation, and parallel programming. Author of 82 scientific works and 11 patents, and holds professor positions at Moscow State University and HSE University.
\end{biography}


\end{document}