The approaches to graph partitioning can be broadly divided into two categories: offline and online partitioning. Offline methods assume complete knowledge of the graph structure before partitioning, whereas online methods assign each newly arriving vertex to a partition without requiring the entire graph to be known in advance.

The current state-of-the-art online graph partitioning algorithm is Fennel, which employs a heuristic objective function to determine the partition to which each incoming vertex should be assigned. Omitting the details presented in the original work \cite{Fennel}, the objective function can be expressed as

\begin{equation*}
    g(P)=\sum_{i=1}^k\left[e(S_i,S_i)-p\binom{|S_i|}{2}\right].
\end{equation*}

where $P$ denotes a graph partitioning, $S_i$ is a storage $i$, $e(S_i,S_i)$ is the number of edges whose endpoints are both contained in $S_i$, and $ p=2\alpha=m\frac{k^{\gamma-1}}{n^\gamma}, \qquad 1\leq\gamma\leq2$.

As noted in the original work, evaluating the complete objective function is unnecessary. Instead, it is sufficient to determine the partition whose objective value increases the most after adding the new vertex. This can be expressed as

\begin{equation}
\delta g(v,S_i)=g(S_1,\ldots,S_i\cup\{v\},\ldots,S_k)-g(S_1,\ldots,S_k),
\label{eq:fennel-delta-big}
\end{equation}

which can be rewritten as

\begin{equation}
\begin{aligned}
\delta g(v,S_i)
={}&
\left[e(S_i\cup\{v\},S_i\cup\{v\})-e(S_i,S_i)\right] \\
&-
\left[
p\binom{|S_i\cup\{v\}|}{2}
-
p\binom{|S_i|}{2}
\right].
\end{aligned}
\label{eq:fennel-delta-small}
\end{equation}

Equation \ref{eq:fennel-delta-small} can be evaluated independently for each partition, assuming that each storage node is capable of performing the required computation. Since the graph is assumed to be undirected, the quantity
$$
e(S_i\cup\{v\},S_i\cup\{v\})-e(S_i,S_i)
$$
is exactly the number of edges connecting the newly added vertex $v$ to vertices already contained in partition $S_i$. The second term depends only on the partition size and can therefore be updated whenever a new vertex is assigned to the partition.

Consequently, the Fennel algorithm produces graph partitions with relatively small edge cuts while requiring only modest computational resources.

Offline partitioning methods generally produce higher-quality partitions but require significantly more computation time and resources. The state-of-the-art framework for offline graph partitioning is METIS, which consists of three stages:

\begin{enumerate}
    \item coarsening;
    \item initial partitioning;
    \item uncoarsening and refinement.
\end{enumerate}

During the uncoarsening stage, the partitioning is refined using the Kernighan--Lin (KL) algorithm. Both the coarsening and uncoarsening stages are computationally expensive, and refinement is performed multiple times during uncoarsening. However, the original METIS publication reports that, given a sufficiently good initial partitioning, the KL algorithm typically requires no more than five iterations to achieve its best refinement \cite{MetisOG}.

Although the original METIS publication observes that only a small number of KL iterations are sufficient when the initial partitioning is of high quality, it does not provide criteria for determining is such a partitioning. Since Fennel has been shown to produce high-quality partitions while operating in an online setting, this motivates the proposed approach of replacing the three-stage METIS partitioning process with Fennel, followed by occasional refinement using the KL algorithm.

The remainder of this paper evaluates the effectiveness of this hybrid approach and investigates the number of KL refinement iterations required when the initial partitioning is generated by Fennel.
